Cell Decompositions for Rank Two Quiver Grassmannians

### 2018-03-01 Grassmannian_cells.tex
Section 5 edits (not yet finished)

  A \emph{2-arrow} of the quiver $Q$ is an ordered pair $V=\big(\Gamma(1),\Gamma(2)\big)$ of full connected subquivers of $Q$, these will be denoted $V:\Gamma(1)\to\Gamma(2)$.
  A \emph{2-quiver} is a pair $\cQ=(Q,Q_2)$ consisting of a quiver $Q$ and a collection $Q_2$ of 2-arrows of $Q$.
  Given a 2-quiver $\cQ$, we call a subset $\beta\subset Q_0$ \emph{strong successor closed in $\cQ$} if it is successor closed in $Q$ and for each 2-arrow $V:\Gamma(1)\to\Gamma(2)$ in $Q_2$ with $\Gamma(1)_0\subset\beta$ we have $\Gamma(2)_0\cap\beta\ne\varnothing$.  
\end{definition}

We introduce a notion of equivalence of $2$-quivers.
\begin{definition}
  \label{def:2equivalence}
  Let $\cQ=(Q,Q_2)$ be a $2$-quiver with a $2$-arrow $V:\Gamma(1)\to\Gamma(2)$ in $Q_2$ such that one of the following conditions is satisfied:
  \begin{enumerate}
    \item $\Gamma(1)$ has precisely one source $p$; 
    \item $\Gamma(2)$ has precisely one sink $q$;
    \item $\Gamma(1)=\{p\}$ and $\Gamma(2)=\{q\}$.
  \end{enumerate}
  Depending on the condition which is satisfied, we define
  \begin{enumerate}
    \item $\cQ_p$ as the $2$-quiver obtained from $\cQ$ when replacing the $2$-arrow $V$ by a $2$-arrow $V_p:\{p\}\to\Gamma(2)$;
    \item $\cQ_q$ as the $2$-quiver obtained from $\cQ$ when replacing the $2$-arrow $V$ by a $2$-arrow $V_q:\Gamma(1)\to \{q\}$;
    \item $\cQ_V$ as the $2$-quiver obtained from $\cQ$ when replacing the $2$-arrow $V$ by a usual arrow $\alpha_V:p\to q$. 
  \end{enumerate}
  This defines a relation on the set of $2$-quivers denoted by $\cQ\to\cQ_p$, $\cQ\to\cQ_q$ and $\cQ\to\cQ_V$ respectively.
  Moreover, it induces an equivalence relation $\sim$ on the set of $2$-quivers when taking the symmetric and transitive closure of this relation. 
\end{definition}

Observe that the vertex sets of equivalent $2$-quivers coincide.
\begin{lemma}
  \label{lem:2equivalence}
  Let $\cQ=(Q,Q_2)$ and $\cQ'=(Q',Q_2')$ be equivalent $2$-quivers.
  If $\beta\subset Q_0$ is strong successor closed in $\cQ$, it also defines a strong successor closed set of vertices in $\cQ$.
  In particular, the number of subsets of $Q_0$ which are strong successor closed in $\cQ$ coincides with the number of subsets of $Q_0'$ which are strong successor closed in $\cQ'$.
\end{lemma}

@@

%\begin{remark}\footnote{Insert a remark that we do not work on the universal cover} 
%  Lemma~\ref{AR} can be generalized to the cases $m\leq 2$.
%  The only technical problem is that $\tau \tilde P^{(k)}_{m+1}$ is no quotient of $\tilde P_{m,k}$ and we have to replace it by the image of the unique morphism to $\tau \tilde P^{(k)}_{m+1}$ which induces the exact sequence. 
%\end{remark}
In the following, we frequently use the notation and conventions of Section~\ref{Lifting}.
The next step is to associate a $2$-quiver $\cQ_{m+1}^{[k]}$ with the lifted truncated preprojective representations 
\[\tilde P_{m+1}^{[k]}:=
  \begin{cases}
    \tilde P_{m+1}^{\{n,n-1,\ldots,n-k+1\}} & \text{ if $m$ is odd;}\\
    \tilde P_{m+1}^{\{1,2,\ldots,k\}} & \text{ if $m$ is even;}
  \end{cases}\] 
for $m\geq 1$ and $0\leq k\leq n-1$.
When $k=0$ above, we take $\tilde P_{m+1}^{[0]}=\tilde P_{m+1}$.
We aim to construct $\cQ_{m+1}^{[k]}$ so that the strong successor closed subsets are in one-to-one correspondence with cells of quiver Grassmannians of $\tilde P_{m+1}^{[k]}$.

Recall that, by Theorem~\ref{celldec}, the cells of the quiver Grassmannians attached to $P_{m+1}^{[k]}:=G(\tilde P_{m+1}^{[k]})$ are in one-to-one correspondence with those attached to the lift $\tilde P_{m+1}^{[k]}$.
Moreover, by Theorem~\ref{thm:truncpp}, the quiver Grassmannians $\Gr_{\tbfe}(P_{m+1}^V)$ of arbitrary truncated preprojective representations $P_{m+1}^V$ only depend on $\tbfe$ and $\udim P_{m+1}^V$.
In short, the $2$-quivers $\mathcal Q_{m+1}^{[k]}$ should be viewed as being attached to any (truncated) preprojective representation of the appropriate dimension.

For building the mentioned $2$-quivers, we use the recursive construction described in Section~\ref{Lifting}.
The following remarks are meant to understand the structure of these $2$-quivers. 
\begin{remark}\mbox{}
  \begin{enumerate}
    \item It will turn out that every vertex of the quiver $\mathcal Q_{m+1}^{[k]}$ uniquely corresponds to a vertex of the universal covering quiver $\widetilde{K(n)}$, but that different vertices of $\cQ_{m+1}^{[k]}$ can correspond to the same vertex of $\widetilde{K(n)}$.
      Also every usual arrow of $\mathcal Q_m^{[k]}$ does correspond to an arrow of $\widetilde{K(n)}$ and thus to an arrow of $K(n)$. In particular, the quiver obtained from $\mathcal Q_m^{[k]}$ when forgetting the $2$-arrows gives rise to a (non-disjoint) union of subquivers of $\widetilde{K(n)}$.

\item Recall that the representation $\tilde P_2^{[n-1]}$ is defined by the support quiver
\[
  \tilde P_2^{[n-1]}=(1,\alpha_1)\xlongleftarrow{\alpha_1}(2,e).%=P_1^{(1)}=j^{(1)}_1\xlongleftarrow{v_1}i^{(1)}_1
\]

%In other words, $P_2^{(n-1)}$ is chosen as be the cokernel of a short exact sequence
%\[
%  \ses{ P_1^{n-1}}{ P_2}{P_2^{(n-1)}}.
%\]
Choosing the lifts $\tilde P_{1,i}$ of $P_1$ supported at $(1,\alpha_i)$ for $2\leq i\leq n$ and using the description of the $\Ext$-groups induced by (\ref{eq:maphomext}), we have 
\begin{align}\label{eq:case2}
  \Ext( P_2^{[n-1]},P_1)\cong \bigoplus_{i=2}^{n}\Ext(\tilde P_2^{[n-1]},\tilde P_{1,i})\cong\langle (2,1)\xrightarrow{\alpha_i}(1,\alpha_i)\mid i=2,\ldots,n\rangle.
\end{align}

\item  For $m\geq 3$, recall that we have $\dim\Hom(P_{m-1},\tau P_m^{[k]})=\dim\Ext(P_m^{[k]},P_{m-1})$ by the Auslander-Reiten formula. This induces isomorphisms
\begin{align}
  \label{eq:homext} 
  \bigoplus_{i=k+1}^n\Hom(\alpha_{i}^{(-1)^{m}}.\tilde P_{m-1},\tau\tilde P_{m}^{[k]})\cong\bigoplus_{i=k+1}^n\Ext(\tilde P_m^{[k]},\alpha_{i}^{(-1)^{m}}. \tilde P_{m-1})\cong \Ext(P_m^{[k]},P_{m-1}).
\end{align}
This means that we can choose a basis of $\Ext(P_m^{[k]},P_{m-1})$ which is compatible with the lifts to the universal covering and which gives a one-to-one correspondence between the basis elements of $\Ext(P_m^{[k]},P_{m-1})$ and $\Hom(P_{m-1},\tau P_m^{[k]})$. 
In view of Corollary~\ref{cor:perpendicular}, we have also an isomorphism $$\Ext(\tilde P_m^{[k]},\tilde P_{m-1,k})\cong\Ext(\tilde P_m^{[k]},\tau\tilde P_m^{[k]}).$$
These isomorphisms will also be present in the structure of the $2$-quivers $\cQ_m^{[k]}$. Finally note that there exists a short exact sequence
\[\ses{\Hom(P_{m-1},P_{m-1})}{\Ext(P_m^{[k]},P_{m-1})}{\Ext(P_m^{[k+1]},P_{m-1})}.\]
Thus a basis of $\Ext(P_m^{[k]},P_{m-1})$ can be obtained by taking the last $k$ basis elements of a basis of $\Ext(P_m^{[n-1]},P_{m-1})$.
\end{enumerate}
\end{remark}

%It turns out that all $2$-quivers can be built from the $2$-quivers of $\tilde P_1$, $\tilde P_2$ and $\tilde P_2^{[n-1]}$. 
Initially, the $2$-quiver $\mathcal Q_1=\cQ_1^{[0]}$ of $\tilde P_1$ is defined by the vertex $(1,e)$. Moreover, we define the translated $2$-quivers $\cQ_{1,i}$ by the vertices $(1,\alpha_i)$. Using (\ref{eq:case2}), we can recursively construct the (truncated) preprojective representation $\tilde P_{2}^{[k]}$ for $k=n-1,\ldots,0$ which are defined by the support quivers
\begin{align}
  \label{coeff}
    \xymatrix@R40pt@C10pt{&(2,e)\ar_{\alpha_1}[ld]\ar^{\alpha_{n-k}}[rd]&\\ (1,\alpha_1)&\cdots&(1,\alpha_{n-k})}
\end{align}

We define the $2$-quiver $\mathcal Q_{2}^{[k]}$  of $\tilde P_2^{[k]}$ for $k=n-1,\ldots,0$ by
\\

\begin{tikzpicture}
\tikzstyle{box} = [rectangle, minimum width=2cm, minimum height=1cm, text centered, draw=black]
\draw (0,0) node (A) {$(1,\alpha_{n-k})$} +(3,0) node (B) {$(1,\alpha_{n-k+1})$}+(3,-.8) node (P1) {\footnotesize$ \mathcal Q_2^{[k+1]}$} +(6,0) node (B1) {$\dots$} +(9,0) node (C) {$(1,\alpha_{2})$} +(9,-.7) node (P3) {\footnotesize$ \mathcal Q_2^{[n-2]}$}+(11.5,0) node (D) {$(1,\alpha_1)$}  +(14,0) node (E) {$(2,e)$} +(11.5,-.6) node (P4) {\footnotesize$\mathcal Q_2^{[n-1]}$}; 
\node (Q1) [draw=black,fit={(D) (E) (P4)}]{};
\node (Q2) [draw=black,fit={(Q1) (C) (P3)}]{};
\node (Q2b)[draw=black,fit={(Q2) (B1) }]{};

@@

\draw[->,red] (Q3)--(A) node[pos=.5,above] {\footnotesize$\alpha_{n-k}$};
\end{tikzpicture}
\\

\noindent
where the $2$-arrows are colored red.
Note that the vertices $(1,\alpha_i)$ are just the $2$-quivers $\cQ_{1,i}$ corresponding to $\tilde P_{1,i}$.
The $2$-quiver $\mathcal Q_2^{[k]}$ is clearly equivalent to the support quiver (\ref{coeff}) thought of as a 2-quiver with no 2-arrows.
In abuse of notation, we also denote the support quiver by $\mathcal Q_{2}^{[k]}$. In order to keep the illustrations and combinatorics simple, we will work with this quiver instead. We also define the translated two quiver $\cQ_{2,i}$ as those obtained from $\cQ_{2}$ by translating all vertices and ($2$-)arrows by $\alpha_i^{-1}$.

The next step is to define the $2$-quivers $\cQ^{[k]}_3$ of the (truncated) preprojective lifts $\tilde P^{[k]}_3$ whence the remaining $2$-quivers attached to the (truncated) preprojectives $\tilde P_m^{[k]}$ can be obtained recursively. First, we define
$$\cQ_3^{[n-1]}:=\alpha_{n}^{-1}.\cQ_2^{[1]},$$
i.e. we translate all vertices - understood as vertices of $\widetilde{K(n)}$ - and $(2)$-arrows by $\alpha_n^{-1}$. Now $\cQ_3^{[k]}$ can be found as a subquiver of $\cQ_{3}$ which is given by connecting $\cQ_3^{[n-1]}$ to $\cQ_{2,i}$ for $i=n-1,\ldots, 1$ in the following way: \\

\begin{tikzpicture}[scale=1.35]
\draw (0,0) node (I1) {$\bullet$} +(1,1) node (J11) {$\bullet$} +(1,.5) node (J12) {$\bullet$} +(1,0.1) node (D1) { $\vdots$}+(1,-.5) node (J1N1) {$\bullet$} +(1,-1) node (J1N) {$\bullet$} ; 
\draw[->] (I1)--(J11) node[pos=.7,above,sloped]{\scriptsize$\alpha_1$};
\draw[->] (I1)--(J12) node[pos=.7,above,sloped]{\scriptsize$\alpha_2$};
\draw[->] (I1)--(J1N1) node[pos=.7,above,sloped]{\scriptsize$\alpha_{n-1}$};
\draw[->] (I1)--(J1N) node[pos=.7,above,sloped]{\scriptsize$\alpha_{n}$};

@@

\end{tikzpicture}
\\

\noindent In abuse of notation, we did not label the vertices in the illustration. Note that the middle vertex of $\mathcal Q_3^{[n-1]}$ corresponds to $(2,\alpha_n^{-1})$ and that all $2$-arrows, which are again colored red, end in a vertex corresponding to $(1,e)$ of $\widetilde{K(n)}$. We again define translated versions $\cQ_{3,i}:=\alpha_i.\cQ_3$ of $\cQ_3$ which again means that we translate $\cQ_{3}$ as a union subquiver contained in $\widetilde{K(n)}$.

>>>>

  A \emph{2-arrow} of the quiver $Q$ is an ordered pair $V=\big(\Gamma(1),\Gamma(2)\big)$ of full connected subquivers of $Q$, these will be denoted $V:\Gamma(1)\to\Gamma(2)$.
  A \emph{2-quiver} is a pair $\cQ=(Q,Q_2)$ consisting of a quiver $Q$ and a collection $Q_2$ of 2-arrows of $Q$.
  Given a 2-quiver $\cQ$, we call a subset $\beta\subset Q_0$ \emph{strong successor closed in $\cQ$} if it is successor closed in $Q$ and for each 2-arrow $V:\Gamma(1)\to\Gamma(2)$ in $Q_2$ with $\Gamma(1)_0\subset\beta$ we have $\Gamma(2)_0\cap\beta\ne\varnothing$.  
\end{definition}
Observe that any quiver can be considered as a 2-quiver with no 2-arrows.

We introduce a notion of equivalence of $2$-quivers.
\begin{definition}
  \label{def:2equivalence}
  Let $\cQ=(Q,Q_2)$ be a $2$-quiver with a $2$-arrow $V:\Gamma(1)\to\Gamma(2)$ in $Q_2$ such that one of the following conditions is satisfied:
  \begin{enumerate}
    \item $\Gamma(1)$ has precisely one source $p$; 
    \item $\Gamma(2)$ has precisely one sink $q$;
    \item $\Gamma(1)=\{p\}$ and $\Gamma(2)=\{q\}$.
  \end{enumerate}
  Depending on the condition which is satisfied, we define
  \begin{enumerate}
    \item $\cQ_p$ as the $2$-quiver obtained from $\cQ$ when replacing the $2$-arrow $V$ by a $2$-arrow $V_p:\{p\}\to\Gamma(2)$;
    \item $\cQ_q$ as the $2$-quiver obtained from $\cQ$ when replacing the $2$-arrow $V$ by a $2$-arrow $V_q:\Gamma(1)\to \{q\}$;
    \item $\cQ_V$ as the $2$-quiver obtained from $\cQ$ when replacing the $2$-arrow $V$ by a usual arrow $\alpha_V:p\to q$. 
      \sayD{It doesn't seem to be part of the definition that there must exist such an arrow in $Q$.}
  \end{enumerate}
  This defines a relation on the set of $2$-quivers denoted by $\cQ\to\cQ_p$, $\cQ\to\cQ_q$ and $\cQ\to\cQ_V$ respectively.
  Moreover, it induces an equivalence relation $\sim$ on the set of $2$-quivers when taking the symmetric and transitive closure of this relation. 
\end{definition}

Observe that the vertex sets of equivalent $2$-quivers coincide.
\begin{lemma}
  \label{lem:2equivalence}
  Let $\cQ=(Q,Q_2)$ and $\cQ'=(Q',Q_2')$ be equivalent $2$-quivers.
  If $\beta\subset Q_0$ is strong successor closed in $\cQ$, it also defines a strong successor closed set of vertices in $\cQ'$.
  In particular, the number of subsets of $Q_0$ which are strong successor closed in $\cQ$ coincides with the number of subsets of $Q_0'$ which are strong successor closed in $\cQ'$.
\end{lemma}

@@

%\begin{remark}\footnote{Insert a remark that we do not work on the universal cover} 
%  Lemma~\ref{AR} can be generalized to the cases $m\leq 2$.
%  The only technical problem is that $\tau \tilde P^{(k)}_{m+1}$ is no quotient of $\tilde P_{m,k}$ and we have to replace it by the image of the unique morphism to $\tau \tilde P^{(k)}_{m+1}$ which induces the exact sequence. 
%\end{remark}
In the following, we frequently use the notation and conventions of Section~\ref{Lifting}.
The next step is to associate a $2$-quiver $\cQ_{m+1}^{[k]}$ with the lifted truncated preprojective representations 
\[\tilde P_{m+1}^{[k]}:=
  \begin{cases}
    \tilde P_{m+1}^{\{n,n-1,\ldots,n-k+1\}} & \text{ if $m$ is odd;}\\
    \tilde P_{m+1}^{\{1,2,\ldots,k\}} & \text{ if $m$ is even;}
  \end{cases}\] 
for $m\geq 1$ and $0\leq k\leq n-1$.
When $k=0$ above, we take $\tilde P_{m+1}^{[0]}=\tilde P_{m+1}$.
We aim to construct $\cQ_{m+1}^{[k]}$ so that the strong successor closed subsets are in one-to-one correspondence with the cells of quiver Grassmannians of~$\tilde P_{m+1}^{[k]}$.

Recall that, by Theorem~\ref{celldec}, the cells of the quiver Grassmannians attached to $P_{m+1}^{[k]}:=G(\tilde P_{m+1}^{[k]})$ are in one-to-one correspondence with those attached to the lift $\tilde P_{m+1}^{[k]}$.
Moreover, by Theorem~\ref{thm:truncpp}, the quiver Grassmannians $\Gr_\bfe(P_{m+1}^V)$ of arbitrary truncated preprojective representations $P_{m+1}^V$ only depend on $\bfe$ and $\udim P_{m+1}^V$.
In short, the $2$-quiver $\mathcal Q_{m+1}^{[k]}$ should be viewed as being attached to any (truncated) preprojective representation of the appropriate dimension.

For building the mentioned $2$-quivers, we use the recursive construction described in Section~\ref{Lifting}.
The following remarks are meant to understand the structure of these $2$-quivers. 
\begin{remark}\mbox{}
  \begin{enumerate}
    \item It will turn out that every vertex of the quiver $\mathcal Q_{m+1}^{[k]}$ uniquely corresponds to a vertex of the universal covering quiver $\widetilde{K(n)}$, but that different vertices of $\cQ_{m+1}^{[k]}$ can correspond to the same vertex of $\widetilde{K(n)}$.
      Also every usual arrow of $\mathcal Q_{m+1}^{[k]}$ does correspond to an arrow of $\widetilde{K(n)}$ and thus to an arrow of $K(n)$.
      In particular, the quiver obtained from $\mathcal Q_{m+1}^{[k]}$ when forgetting the $2$-arrows gives rise to a (possibly non-disjoint) union of subquivers of $\widetilde{K(n)}$.

  \item Recall that the representation $\tilde P_2^{[n-1]}$ is defined by the support quiver
    \[\tilde P_2^{[n-1]}=(1,\alpha_1)\xlongleftarrow{\alpha_1}(2,e).\]

    Choosing the lifts $\tilde P_{1,i}$ of $P_1$ supported at $(1,\alpha_i)$ for $2\leq i\leq n$ and using the description of the $\Ext$-groups induced by (\ref{eq:maphomext}), we have 
    \begin{align}
      \label{eq:case2}
      \Ext\big(P_2^{[n-1]},P_1\big)
      \cong\bigoplus_{i=2}^{n}\Ext\big(\tilde P_2^{[n-1]},\tilde P_{1,i}\big)
      \cong\big\langle (2,1)\xrightarrow{\alpha_i}(1,\alpha_i)\mid i=2,\ldots,n\big\rangle.
    \end{align}

  \item  For $m\geq 2$, recall that we have $\dim\Hom\big(P_m,\tau P_{m+1}^{[k]}\big)=\dim\Ext\big(P_{m+1}^{[k]},P_m\big)$ by the Auslander-Reiten formula.
    This induces isomorphisms
    \begin{align}
      \label{eq:homext} 
      \bigoplus_{i=k+1}^n \Hom\big(\alpha_{i}^{(-1)^{m+1}}.\tilde P_m,\tau\tilde P_{m+1}^{[k]}\big)
      \cong\bigoplus_{i=k+1}^n \Ext\big(\tilde P_{m+1}^{[k]},\alpha_{i}^{(-1)^{m+1}}.\tilde P_m\big)
      \cong\Ext\big(P_{m+1}^{[k]},P_m\big).
    \end{align}
    This means that we can choose a basis of $\Ext\big(P_{m+1}^{[k]},P_m\big)$ which is compatible with the lifts to the universal covering and which gives a one-to-one correspondence between the basis elements of $\Ext\big(P_{m+1}^{[k]},P_m\big)$ and $\Hom\big(P_m,\tau P_{m+1}^{[k]}\big)$. 
    In view of Corollary~\ref{cor:perpendicular}, we have also an isomorphism 
    \[\Ext\big(\tilde P_{m+1}^{[k]},\tilde P_{m,k}\big)\cong\Ext\big(\tilde P_{m+1}^{[k]},\tau\tilde P_{m+1}^{[k]}\big).\]
    These isomorphisms will also be present in the structure of the $2$-quivers $\cQ_{m+1}^{[k]}$.
    Finally note that there exists a short exact sequence
    \[\ses{\Hom(P_m,P_m)}{\Ext\big(P_{m+1}^{[k]},P_m\big)}{\Ext\big(P_{m+1}^{[k+1]},P_m\big)}.\]
    Thus a basis of $\Ext\big(P_{m+1}^{[k]},P_m\big)$ can be obtained by taking the last $k$ basis elements of a basis of $\Ext\big(P_{m+1}^{[n-1]},P_m\big)$.
  \end{enumerate}
\end{remark}

The $2$-quivers $\cQ_{m+1}^{[k]}$ will be built inductively.
To begin, the $2$-quiver $\mathcal Q_1=\cQ_1^{[0]}$ of $\tilde P_1$ is defined simply as the quiver consisting of a single vertex $(1,e)$.
Moreover, we define the translated $2$-quivers $\cQ_{1,i}$ by the vertices $(1,\alpha_i)$.
Using (\ref{eq:case2}), we recursively construct the (truncated) preprojective representations $\tilde P_{2}^{[k]}$ for $k=n-1,\ldots,0$ using their support quivers
\begin{align}
  \label{coeff}
    \xymatrix@R40pt@C10pt{&(2,e)\ar_{\alpha_1}[ld]\ar^{\alpha_{n-k}}[rd]&\\ (1,\alpha_1)&\cdots&(1,\alpha_{n-k})}
\end{align}

We define the $2$-quiver $\mathcal Q_{2}^{[k]}$  of $\tilde P_2^{[k]}$ for $k=n-1,\ldots,0$ by
\[
\begin{tikzpicture}
\tikzstyle{box} = [rectangle, minimum width=2cm, minimum height=1cm, text centered, draw=black]
\draw (0,0) node (A) {$(1,\alpha_{n-k})$} +(3,0) node (B) {$(1,\alpha_{n-k+1})$}+(3,-.8) node (P1) {\footnotesize$ \mathcal Q_2^{[k+1]}$} +(6,0) node (B1) {$\dots$} +(9,0) node (C) {$(1,\alpha_{2})$} +(9,-.7) node (P3) {\footnotesize$ \mathcal Q_2^{[n-2]}$}+(11.5,0) node (D) {$(1,\alpha_1)$}  +(14,0) node (E) {$(2,e)$} +(11.5,-.6) node (P4) {\footnotesize$\mathcal Q_2^{[n-1]}$}; 
\node (Q1) [draw=black,fit={(D) (E) (P4)}]{};
\node (Q2) [draw=black,fit={(Q1) (C) (P3)}]{};
\node (Q2b)[draw=black,fit={(Q2) (B1) }]{};

@@

\draw[->,red] (Q3)--(A) node[pos=.5,above] {\footnotesize$\alpha_{n-k}$};
\end{tikzpicture}
\]
where the $2$-arrows are colored red.
Note that the vertices $(1,\alpha_i)$ are just the $2$-quivers $\cQ_{1,i}$ corresponding to $\tilde P_{1,i}$.
The $2$-quiver $\mathcal Q_2^{[k]}$ is clearly equivalent to the support quiver (\ref{coeff}) thought of as a 2-quiver with no 2-arrows.
In abuse of notation, we also denote the support quiver by $\mathcal Q_{2}^{[k]}$.
In order to keep the illustrations and combinatorics simple, we will work with this quiver instead.
We also define the translated two quivers $\cQ_{2,i}$ as those obtained from $\cQ_2$ by translating all vertices and ($2$-)arrows by $\alpha_i^{-1}$.

The next step is to define the $2$-quivers $\cQ^{[k]}_3$ of the (truncated) preprojective lifts $\tilde P^{[k]}_3$ whence the remaining $2$-quivers attached to the (truncated) preprojectives $\tilde P_m^{[k]}$ can be obtained recursively.
First, we define
\[\cQ_3^{[n-1]}:=\alpha_{n}^{-1}.\cQ_2^{[1]},\]
i.e. we translate all vertices -- understood as vertices of $\widetilde{K(n)}$ -- and (2-)arrows by $\alpha_n^{-1}$.
Then $\cQ_3^{[k]}$ can be found as a sub-2-quiver of $\cQ_3$ which is constructed recursively by connecting $\cQ_3^{[i]}$ to $\cQ_{2,i}$ for $i=n-1,\ldots, 1$ in the following way: \\
\[
\begin{tikzpicture}[scale=1.35]
  \draw (0,0) node (I1) {$\bullet$} +(1,1) node (J11) {$\bullet$} +(1,.5) node (J12) {$\bullet$} +(1,0.1) node (D1) { $\vdots$}+(1,-.5) node (J1N1) {$\bullet$} +(1,-1) node (J1N) {$\bullet$} ; 
  \draw[->] (I1)--(J11) node[pos=.7,above,sloped]{\scriptsize$\alpha_1$};
  \draw[->] (I1)--(J12) node[pos=.7,above,sloped]{\scriptsize$\alpha_2$};
  \draw[->] (I1)--(J1N1) node[pos=.7,above,sloped]{\scriptsize$\alpha_{n-1}$};
  \draw[->] (I1)--(J1N) node[pos=.7,above,sloped]{\scriptsize$\alpha_{n}$};

@@

\end{tikzpicture}
\] 
To avoid cluttering the diagram, we did not label the vertices in the illustration.
Observe that the middle vertex of $\mathcal Q_3^{[n-1]}$ corresponds to $(2,\alpha_n^{-1})$ and that the target of the $2$-arrow, again colored red, into $\cQ_{2,n-1}$ is the vertex corresponding to $(1,e)$ of $\widetilde{K(n)}$.
In general, the 2-arrow from $\cQ_3^{[i]}$ into $\cQ_{2,i}$ has target the vertex corresponding to $(1,e)$ in $\widetilde{K(n)}$.
We again define translated versions $\cQ_{3,i}:=\alpha_i.\cQ_3$ of $\cQ_3$ which again means that we translate $\cQ_{3}$ as a union subquiver contained in $\widetilde{K(n)}$.

\begin{remark} Recall that $\tilde P_3^{[n-1]}=\alpha_n^{-1}.\tilde P_2^{[1]}$. Moreover, (\ref{eq:homext}) for $m=3$ yields 
$$\Ext(P_2^{[1]},P_2)\cong\Ext(P_3^{[n-1]},P_2)\cong\bigoplus_{i=1}^{n-1}\Ext(\tilde P_3^{[n-1]},\alpha_i^{-1}\tilde P_2).$$
This decomposition induces a basis of $\Ext(P_3^{[n-1]},P_2)$, each basis element given by the linear map $$(2,\alpha_n^{-1})\xlongrightarrow{\alpha_n}(1,e)\in\Hom_{\CC}((\tilde P_2^{[1]})_{(2,\alpha_n^{-1})},(\alpha_i^{-1}\tilde P_2)_{(1,e)})$$
for $i=1,\ldots,n-1$. Recall that the representation $\tau\tilde P_3^{[k]}$ is given by 
\[ \xymatrix@R40pt@C10pt{&(1,e)&\\ (2,\alpha_1^{-1})\ar_{\alpha_1}[ru]&\cdots&(2,\alpha_{k}^{-1})\ar^{\alpha_{k}}[lu]}.\]
Note that the image of the homomorphism corresponding to the basis element spanning 
\[\Hom(\alpha_{k}^{-1}.\tilde P_{2},\tau\tilde P_{m}^{[k]})\cong\Ext(\tilde P_3^{[n-1]},\alpha_k^{-1}\tilde P_2)\]
corresponds to the subquiver $(2,\alpha_k^{-1})\xrightarrow{\alpha_k} (1,e)$.
This translates to the fact that $\cQ_3^{[k]}$ is glued to the image of the homomorphism $\tilde P_{2,k}\to \tau \tilde P_3^{[k]}$ which is of dimension $(1,1)$. In view of Lemma~\ref{lem:2equivalence}, we forgo inserting the corresponding rectangles around the subquiver and just connect the $2$-arrows to the sinks of the corresponding subquivers of dimension $(1,1)$. 
%In summary, the chosen basis of $\Ext(P_3^{[n-1]},P_2)$ motivated the definition of the $2$-quiver $\mathcal Q_3=\mathcal Q_3^{[0]}$ of $\tilde P_3$ and the $2$-quivers $\mathcal Q_3^{[k]}$ for $k=n-1,\ldots,1$.
\end{remark}
%It remains to consider the case when $m$ is even. Lemma~\ref{AR} yields
%\begin{align}\label{eq:case2}
 %\Hom(P_{m-1},\tau \tilde P_{m}^{[k]})\cong\bigoplus_{i=k+1}^{n}\Hom(\alpha_i\tilde P_{m-1},\tau \tilde P_{m}^{[k]})\cong \bigoplus_{i=k+1}^{n}\Ext(\tilde P_m^{[k]},\alpha_i\tilde P_{m-1})\cong\Ext(P_m^{[k]},P_{m-1}).
%\end{align}
Now we can recursively build the $2$-quivers $\cQ_{m+1}^{[k]}$ of $\tilde P_{m+1}^{[k]}$ for $m\geq 3$ and $k=n-1,\ldots,0$. 
%This construction is motivated by considering the natural basis of $\Ext(P_m^{[n-1]},P_{m-1})$ induced by the decomposition (\ref{eq:homext}). 
%As we have a one-to-one correspondence between basis elements of $\Hom(P_{m-1},\tau P_m^{[k]})$ and $\Ext(P_m^{[k]},P_{m-1})$ when passing to the universal covering quiver, we can proceed as before.
%Recall that we have $\udim P_m^{[k]}=\udim P_{m-1}^{[1]}+(n-k-1)\udim P_{m-1}$.
Let us assume that we already constructed the $2$-quivers $\cQ_{l}^{[j]}$ of $P_{l}^{[j]}$ for $l\leq m$, $j=0,\ldots, n-1$ and $l=m+1$, $j=n-1,\ldots,k$. As before, we define the translated $2$-quivers $\cQ_{m,i}=\alpha_i^{(-1)^{m+1}}.\cQ_m$.
Moreover, we define 
\[\cQ_{m+1}^{[n-1]}:=\begin{cases}\alpha_{n}^{-1}.\cQ_{m}^{[1]}\text{ if }m\text{ is even}\\\alpha_{1}.\cQ_{m}^{[1]}\text{ if }m\text{ is odd}\end{cases}.\]
